Interval Probability and Measurement for Fuzzy Quantum Theories

### 2016-11-23 prob.tex
discreteGBKS.bib Add citations, and cited articles...
"D. Aerts, T. Durt, B. Van Bogaert, A physical example of quantum fuzzy sets, and the classical limit.pdf" Added...
discreteGBKS.bib Add citation, and change encoding to utf8

%% LyX 2.2.1 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass{article}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{verbatim}
\usepackage{mathrsfs}
\usepackage{url}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{graphicx}

@@

@@

Fuzzy quantum mechanics: 
\begin{itemize}
\item \url{http://cds.cern.ch/record/518511/files/0107054.pdf} 
\item \url{http://link.springer.com/chapter/10.1007%2F978-3-642-35644-5_18#page-1} 
\item \url{http://link.springer.com/chapter/10.1007%2F978-3-540-93802-6_20#page-1} 
\item \url{http://www.du.edu/nsm/departments/mathematics/media/documents/preprints/m0412.pdf} 
\item \url{http://www.space-lab.ru/files/pages/PIRT_VII-XII/pages/text/PIRT_X/Bobola.pdf} 
\item \url{http://www.vub.ac.be/CLEA/aerts/publications/1993LiptovskyJan.pdf} 
\end{itemize}
\noindent Pseudo-randomness: 
\begin{itemize}
\item \url{https://people.csail.mit.edu/silvio/Selected%20Scientific%20Papers/Pseudo%20Randomness/How_To_Generate_Cryptographically_Strong_Sequences_Of_Pseudo-Random_Bits.pdf}:
``the randomness of an event is relative to a specific model of computation
with a specified amount of computing resources.'' 
\item Another version \url{https://pdfs.semanticscholar.org/3e9c/5f6f48d9ef426655dc799e9b287d754e86c1.pdf} 
\end{itemize}
%%%%%

>>>>

%% LyX 2.2.1 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[english]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{verbatim}
\usepackage{mathrsfs}
\usepackage{url}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{graphicx}

@@

\usepackage{babel}

@@

Fuzzy quantum mechanics: 
\begin{itemize}
\item \url{http://cds.cern.ch/record/518511/files/0107054.pdf} \cite{GranikCaulfield2001}\\
\yutsung{The journal didn't put the given volume online... Add arXiv
version as well, and request an inter-librarian loan...}
\item \url{http://link.springer.com/chapter/10.1007%2F978-3-642-35644-5_18#page-1}
\cite{Pykacz2013}
\item \url{http://link.springer.com/chapter/10.1007%2F978-3-540-93802-6_20#page-1}
\cite{SNL2009}
\item \url{http://www.du.edu/nsm/departments/mathematics/media/documents/preprints/m0412.pdf}
\cite{Gudder2005}\\
\yutsung{Cannot get the published version online. Request an inter-librarian
loan.}
\item \url{http://www.space-lab.ru/files/pages/PIRT_VII-XII/pages/text/PIRT_X/Bobola.pdf}
\\
\yutsung{Doesn't find this paper anywhere else except in this URL...
It seems that it doesn't appear in author's homepage, and I am not
sure if I found their institution's web page... Very strange...}
\item \url{http://www.vub.ac.be/CLEA/aerts/publications/1993LiptovskyJan.pdf}
\cite{aerts1993physical}
\item \cite{RiecanNeubrunn1997}\\
\yutsung{Might related. Get this book when I google ``Fuzzy Gleason's
Theorem''...}
\end{itemize}
\noindent Pseudo-randomness: 
\begin{itemize}
\item \url{https://people.csail.mit.edu/silvio/Selected%20Scientific%20Papers/Pseudo%20Randomness/How_To_Generate_Cryptographically_Strong_Sequences_Of_Pseudo-Random_Bits.pdf}:
``the randomness of an event is relative to a specific model of computation
with a specified amount of computing resources.'' \cite{BlumMicali1984}
\item Another version \url{https://pdfs.semanticscholar.org/3e9c/5f6f48d9ef426655dc799e9b287d754e86c1.pdf} 
\end{itemize}
%%%%%
